Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-02 paper/structureScene.tex
Add some references for conv nets

Addressing this task first requires the ability to capture meaningful aspects within the signal at small time-scales.
In other words, how do we represent an extract of the auditory scene signal over a sub-second interval?
A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years in music information retrieval \cite{logan} and environmental audio processing \cite{aucouturier2007bag}.
A richer set of features is found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014,chudacek}.
This is because the scattering transform cascades wavelet convolutions and pointwise nonlinearities, thus imitating the architecture of a convolutional neural network \cite{} \ja{some relevant refs on dnns 4 audio}.

>>>>

Addressing this task first requires the ability to capture meaningful aspects within the signal at small time-scales.
In other words, how do we represent an extract of the auditory scene signal over a sub-second interval?
A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years in music information retrieval \cite{logan} and environmental audio processing \cite{aucouturier2007bag}.
A richer set of features is found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014,chudacek}.
This is because the scattering transform cascades wavelet convolutions and pointwise nonlinearities, thus imitating the architecture of a convolutional neural network \cite{lee,lostanlen-deep-spiral,soundnet,arandjelovic-zisserman}.
